---
title: "Introduction to lordifMultiverse"
author: "Constantin Yves Plessen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to lordifMultiverse}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction to lordifMultiverse

The `lordifMultiverse` package provides a comprehensive toolkit for detecting differential item functioning (DIF) across multiple criteria and thresholds. This package is designed to facilitate the exploration of DIF in a multiverse analysis context, allowing users to assess the robustness of their findings across a range of analytical decisions.

<br>

## Installation

To install the latest version of `lordifMultiverse` from GitHub, use the following commands:

```{r, eval=FALSE}
devtools::install_github("cyplessen/lordifMultiverse")
```

<br>

# Basic Usage

## lordif_multiverse Function

The lordif_multiverse function is the core of the package, enabling users to perform DIF analysis across various criteria and thresholds. Here's a basic example of how to use it:

### Load the package
```{r}
library(lordifMultiverse)
```


### Load data

As an example, I use data from the lordif package.
```{r}
# Assuming `items` is a dataframe of item responses and `group` is a vector defining group memberships
data(Anxiety, package = "lordif")
items_anxiety <- Anxiety[paste("R", 1:29, sep = "")]
group_age <- Anxiety$age
```

### Run the lordif_multiverse analysis
```{r results='hide'}
results <- lordif_multiverse(items = items_anxiety, group = group_age)
```


```{r}
results
```

<br>

# Visualizing Results

To visualize the results of the lordif_multiverse function, you can use the plot_lordif_multiverse function. This function creates a comprehensive plot showing how many items were flagged for DIF across different criteria and thresholds.

```{r, fig.width=8, fig.height=8}
# Assuming `results` contains the output from lordif_multiverse
plot_lordif_multiverse(results, items_anxiety)
```

<br>

# Advanced Usage

## Customizing Criteria and Thresholds

You can customize the criteria and thresholds for the lordif_multiverse analysis by creating a criteria_thresholds list. This allows for a highly flexible analysis tailored to specific research questions.

## Example of customizing criteria and thresholds 

```{r results='hide'}
custom_criteria <- list(
  Chisqr = c(0.01, 0.05),
  Beta = c(0.1, 0.2),
  CoxSnell = c(0.03, 0.04)
)

results_custom <- lordif_multiverse(items = items_anxiety, 
                                    group = group_age, 
                                    custom_criteria_thresholds = custom_criteria, 
                                    verbose = TRUE)
```


```{r, fig.width=8, fig.height=8}
results_custom

plot_lordif_multiverse(results_custom, items_anxiety)
```

<br>

# Conclusion

The lordifMultiverse package offers a powerful and flexible approach to exploring differential item functioning in psychological and educational assessments. By allowing for the analysis across multiple criteria and thresholds, it enables researchers to conduct thorough and robust DIF analyses.

For more information, please refer to the function documentation within the package.